\bf Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-08-21 ProbabilisticCoherence.tex
converted to JASA style

\documentclass[a4paper, 11pt]{article}
\usepackage{monashwp}
\usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx,paralist}
\usepackage{mathrsfs, float, booktabs,todonotes,amsthm}
\usepackage[bb=boondox]{mathalfa}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning,shapes,fit,calc}
\usepackage{amsfonts}
\hypersetup{citecolor=blue,linkcolor=blue,urlcolor=blue}
\DeclareNameAlias{sortname}{last-first}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcolumntype{L}{>{$}l<{$}} % math-mode version of "l" column type
\def\mathbi#1{\textit{ #1}}
\def\mathB#1{\textbf{ #1}}
\def\E{\text{E}}
\def\var{\text{Var}}
\mathtoolsset{showonlyrefs=true}

@@

\title{Probabilistic Forecasts in Hierarchical~Time~Series}
\author{Puwasala Gamakumara\\ Anastasios Panagiotelis\\ George Athanasopoulos\\ Rob J Hyndman}

\addresses{\textbf{Puwasala Gamakumara}\\
  Department of Econometrics and Business Statistics,\\
  Monash University,\\ VIC 3800, Australia.\\
  Email: Puwasala.Gamakumara@monash.edu \\[1cm]
  \textbf{Anastasios Panagiotelis}\\
  Department of Econometrics and Business Statistics,\\
  Monash University,\\ VIC 3800, Australia.\\
  Email: Anastasios.Panagiotelis@monash.edu\\[1cm]
  \textbf{George Athanasopoulos}\\
  Department of Econometrics and Business Statistics,\\
  Monash University,\\ VIC 3800, Australia.\\
  Email: George.Athanasopoulos@monash.edu\\[1cm]
  \textbf{Rob J Hyndman}\\
  Department of Econometrics and Business Statistics,\\
  Monash University,\\ VIC 3800, Australia.\\
  Email: Rob.Hyndman@monash.edu}

\lfoot{\sf Gamakumara, Panagiotelis, Athanasopoulos \& Hyndman: \today}

@@

\maketitle

@@

@@

\begin{table}[!h]
	\caption{Summary of reconciliation methods that are projections. Here, $\hat{\bm{W}}^{sam}$ is the variance covariance matrix of one-step ahead forecast errors, $\hat{\bm{W}}^{shr}$ is a shrinkage estimator more suited to large dimensions proposed by \citet{Schafer2005}, $\hat{\bm{W}}^{wls}$ is the diagonal matrix with diagonal elements $w_{ii}$, and $\tau = \frac{\sum_{i \neq j}\hat{\var}(\hat{w}_{ij})}{\sum_{i \neq j}{\hat{w}}^2_{ij}}$, where $w_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{W}}^{sam}$.}\label{table:2}
	\centering\setstretch{1.5}
	\begin{tabular}{lll}
		\toprule
		\textbf{Method} & \textbf{$\bm{W}$} & \textbf{ $\bm{R}'_\bot$}      \\
		\midrule
		OLS             &
		$\bm{I}$  &
		$\bm{S}'$  \\
		MinT(Sample)    &
		$\hat{\bm{W}}^{sam}$ &
		$\bm{S}'(\hat{\bm{W}}^{sam})^{-1}$ \\
		MinT(Shrink)    &
		$\tau\text{Diag}(\hat{\bm{W}}^{sam}) + (1-\tau)\hat{\bm{W}}^{sam}$ &
		$\bm{S}'(\hat{\bm{W}}^{shr})^{-1}$ \\
		WLS       &
		$\text{Diag}(\hat{\bm{W}}^{shr})$ &
		$\bm{S}'(\hat{\bm{W}}^{wls})^{-1}$ \\
		\bottomrule
	\end{tabular}
\end{table}

@@

\newpage
\printbibliography
\end{document}

>>>>

%&latex
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL

\usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx,paralist}
\usepackage{mathrsfs, float, booktabs,todonotes,amsthm}
\usepackage[bb=boondox]{mathalfa}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning,shapes,fit,calc}
\usepackage{amsfonts}

\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{0}

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{-.3in}%
\addtolength{\topmargin}{-.8in}%

\DeclareMathOperator*{\argmin}{arg\,min}
\newcolumntype{L}{>{$}l<{$}} % math-mode version of "l" column type
\def\mathbi#1{\textit{ #1}}
\def\mathB#1{\textbf{ #1}}
\def\E{\text{E}}
\def\var{\text{Var}}

@@

@@

	%\bibliographystyle{natbib}

	\def\spacingset#1{\renewcommand{\baselinestretch}%
		{#1}\small\normalsize} \spacingset{1}

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	\if1\blind
	{
		\title{\bf Probabilistic Forecasts in Hierarchical~Time~Series}
		\author{Puwasala Gamakumara\thanks{
				The authors gratefully acknowledge \textit{please remember to list all relevant funding sources in the unblinded version}}\hspace{.2cm}\\
			    Department of Econometrics and Business Statistics,\\
			    Monash University,\\ VIC 3800, Australia.\\
			    Email: Puwasala.Gamakumara@monash.edu \\
			    and \\
			    Anastasios Panagiotelis\\
			    Department of Econometrics and Business Statistics,\\
		    	Monash University,\\ VIC 3800, Australia.\\
			    Email: Anastasios.Panagiotelis@monash.edu \\
			    and \\
		        George Athanasopoulos\\
		        Department of Econometrics and Business Statistics,\\
		        Monash University,\\ VIC 3800, Australia.\\
		        Email: george.athanasopoulos@monash.edu \\
		        and \\
	            Rob J Hyndman\\
	            Department of Econometrics and Business Statistics,\\
	            Monash University,\\ VIC 3800, Australia.\\
	            Email: rob.hyndman@monash.edu \\}
		\maketitle
	} \fi

	\if0\blind
	{
		\bigskip
		\bigskip
		\bigskip
		\begin{center}
			{\LARGE\bf Probabilistic Forecasts in Hierarchical~Time~Series}
		\end{center}
		\medskip
	} \fi

	\bigskip

@@

\noindent%
{\it Keywords:}  3 to 6 keywords, that do not appear in the title
\vfill

\newpage
\spacingset{1.45} % DON'T change the spacing!

@@

\begin{table}[!h]
	\caption{Summary of reconciliation methods that are projections. Here, $\hat{\bm{W}}^{sam}$ is the variance covariance matrix of one-step ahead forecast errors, $\hat{\bm{W}}^{shr}$ is a shrinkage estimator more suited to large dimensions proposed by \citet{Schafer2005}, $\hat{\bm{W}}^{wls}$ is the diagonal matrix with diagonal elements $w_{ii}$, and $\tau = \frac{\sum_{i \neq j}\hat{\var}(\hat{w}_{ij})}{\sum_{i \neq j}{\hat{w}}^2_{ij}}$, where $w_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{W}}^{sam}$.}\label{table:2}
	\centering
	\begin{tabular}{lll}
		\toprule
		\textbf{Method} & \textbf{$\bm{W}$} & \textbf{ $\bm{R}'_\bot$}      \\
		\midrule
		OLS             &
		$\bm{I}$  &
		$\bm{S}'$  \\
		MinT(Sample)    &
		$\hat{\bm{W}}^{sam}$ &
		$\bm{S}'(\hat{\bm{W}}^{sam})^{-1}$ \\
		MinT(Shrink)    &
		$\tau\text{Diag}(\hat{\bm{W}}^{sam}) + (1-\tau)\hat{\bm{W}}^{sam}$ &
		$\bm{S}'(\hat{\bm{W}}^{shr})^{-1}$ \\
		WLS       &
		$\text{Diag}(\hat{\bm{W}}^{shr})$ &
		$\bm{S}'(\hat{\bm{W}}^{wls})^{-1}$ \\
		\bottomrule
	\end{tabular}
\end{table}

@@

\newpage

\bibliographystyle{agsm}

\end{document}
